%-------------------------
% Resume in Latex
% Author : Adapted for Suhas R G
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% Uncomment your preferred font option
% \usepackage[sfdefault]{FiraSans} % sans-serif
% \usepackage[default]{sourcesanspro} % serif

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Suhas R G} \\ \vspace{1pt}
    Bengaluru, Karnataka \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 6364695019 ~ \href{mailto:rgsuhas6364@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{rgsuhas6364@gmail.com}} ~ 
    \href{https://linkedin.com/in/rgsuhas}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/rgsuhas}}  ~
    \href{https://github.com/rgsuhas}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/rgsuhas}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {HKBK College of Engineering}{Dec. 2022 -- May 2026}
      {B.E. in Computer Science and Engineering}{Bengaluru, Karnataka}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    \begin{multicols}{3}
        \begin{itemize}[itemsep=-5pt, parsep=3pt]
            \item Data Structures
            \item Database Management
            \item Algorithms Analysis
            \item Machine Learning
            \item Artificial Intelligence
            \item Data Science
            \item Statistics
            \item Software Methodology
        \end{itemize}
    \end{multicols}
    \vspace*{2.0\multicolsep}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Analytics Job Simulation}{Nov 2024 -- Dec 2024}
      {TATA, Forage}{Remote}
      \resumeItemListStart
        \resumeItem{Completed a comprehensive data analysis project focusing on real-world applications of data processing and visualization.}
        \resumeItem{Demonstrated skills in data cleaning, data visualization, and report presentation.}
        \resumeItem{Tools Used: MS Excel, Power BI, MySQL.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Science Internship}{Jan 2025 -- Present}
      {Saara Inc}{Bangalore}
      \resumeItemListStart
        \resumeItem{Assisting in collecting, cleaning, and preprocessing data for analysis.}
        \resumeItem{Developing predictive models and implementing machine learning algorithms.}
        \resumeItem{Collaborating with cross-functional teams to deliver data-driven solutions.}
        \resumeItem{Tools Used: Python, R, SQL, Tableau, Power BI.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{Drive Downloader} $|$ \emph{Go, Google Drive API, OAuth2}}{Nov 2024}
          \resumeItemListStart
            \resumeItem{Developed a command-line tool to interact with Google Drive, enabling automated file downloads.}
            \resumeItem{Integrated OAuth2 and service account authentication for user and automated access.}
            \resumeItem{Implemented file listing and filtering capabilities with metadata support.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Image Filter Application} $|$ \emph{Python, Streamlit, OpenCV}}{Dec 2024}
          \resumeItemListStart
            \resumeItem{Created a web app to apply artistic filters to images, enhancing user interactivity and usability.}
            \resumeItem{Implemented dark and light modes for accessibility and visual appeal.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, R, SQL, Go, JavaScript, C} \\
     \textbf{Tools}{: MS Excel, Tableau, Power BI, Streamlit, Docker, Postman, gRPC} \\
     \textbf{Technologies}{: Machine Learning, Data Cleaning, Data Visualization, Predictive Modeling, Agile (Scrum)} \\
    }}
 \end{itemize}

%-----------COURSES AND CERTIFICATIONS-----------
\section{Courses and Certifications}
    \resumeSubHeadingListStart
        \resumeSubheading{Google Data Analytics Professional Certificate}{Jun 2024}{Coursera}{Verified by Google}
            \resumeItemListStart
                \resumeItem{Completed 8 courses covering data preparation, cleaning, visualization, and analysis.}
                \resumeItem{Tools Proficiency: Spreadsheets, SQL, Tableau, R Programming.}
                \resumeItem{Capstone: Completed a case study demonstrating data-driven decision-making.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
