%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Suhas R G} \\ \vspace{1pt}
    Bengaluru, Karnataka \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 6364695019 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{rgsuhas6364@gmail.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/rgsuhas}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/rgsuhas}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {HKBK Collge of Engineering}{Dec. 2022 -- May 2026}
      {Computer Science and Engineering}{Bengaluru, Karnataka}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Software Methodology
                \item Algorithms Analysis
                \item Database Management
                \item Artificial Intelligence
                \item Computer Networks
                \item Project Management
                \item OOPs with Java
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Open CLM}{October 2024 - Present}
      {Software Engineer}{Bengaluru, Karnataka}
      \resumeItemListStart
        \resumeItem{Designed and implemented a \textbf{Git-service} for managing user files, ensuring seamless interaction across the stack. }
        \resumeItem{Developed scalable \textbf{gRPC APIs} to enable communication between the backend and other services in a distributed system. }
        \resumeItem{Integrated backend APIs with a \textbf{React-based web application}, optimizing frontend-backend communication for a user-centric experience. }
        \resumeItem{Wrote \textbf{GitHub workflows} to streamline CI/CD processes, enhancing deployment efficiency. Learned and applied \textbf{Git and GitHub} best practices for version control and collaboration.}
    \resumeItem{ Actively participated in \textbf{Scrum ceremonies} and worked in \textbf{sprint-based} cycles to deliver features in a fast-paced environment.}
    \resumeItem{Collaborated in a \textbf{cross-functional team} of 5, driving the project from concept to MVP.  }
      \resumeItemListEnd
\textbf{Technical Stack}: Golang (Go), gRPC, REST APIs, React.js, Microservices, Git/GitHub,  Agile (Scrum, Sprints) .
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{Image Filter Application} $|$ \emph{Python, Streamlit, OpenCV}}{December 2024}
          \resumeItemListStart
            \resumeItem{Developed a Streamlit-based web application that allows users to upload images and apply artistic filters such as watercolor sketch, pencil sketch, cartoon, sepia, HDR, and sharpening.}
            \resumeItem{Implemented dark and light modes to improve accessibility and enhance user experience.}
            \resumeItem{Deployed the application on the Streamlit platform, enabling seamless and user-friendly access.}
            \resumeItem{Utilized OpenCV for efficient image processing and incorporated interactive features for a streamlined user workflow.}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {\textbf{Drive Downloader} $|$ \emph{Go, Google Drive API, OAuth2}}{November 2024}
          \resumeItemListStart
            \resumeItem{Developed a Go-based command-line tool to interact with Google Drive, enabling users or service accounts to download files and folders seamlessly.}
            \resumeItem{Implemented OAuth2 authentication for user-based access and service account authentication for automated scripts and background processes.}
            \resumeItem{Provided file and folder listing functionality with filtering options based on file type, name, and metadata.}
            \resumeItem{Integrated error handling mechanisms to manage permission and access issues effectively.}
            \resumeItem{Designed the tool for automation and scalability, making it suitable for background processes and large-scale file management in Google Drive.}
          \resumeItemListEnd
     % --------new projects here-------------     
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go (Golang), Python, JavaScript, HTML/CSS, SQL, C} \\
     \textbf{Developer Tools}{: VS Code, Git, GitHub, Docker, Streamlit, Postman, gRPC, Google Cloud Platform} \\
     \textbf{Technologies/Frameworks}{: React.js, Linux, Microservices, Jenkins, CI/CD, Agile (Scrum, Sprints), OpenCV} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Courses and Certificates}
    \resumeSubHeadingListStart
        \resumeSubheading{Web Development Course}{Nov 2024 -- Present}{By: Hithesh Chooudery on Udemy}{}
            \resumeItemListStart
                \resumeItem{Gained proficiency in full-stack development, covering HTML, CSS, Tailwind, Node.js, React, MongoDB, Prisma, and deployment techniques.}
                \resumeItem{Mastered the JavaScript ecosystem and its frameworks to build scalable and efficient web applications.}
                \resumeItem{Developed skills to create and manage projects as a full-stack developer for companies or freelance opportunities.}
                \resumeItem{Explored advanced topics such as MERN stack, Git, and modern web development practices.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
